Stochastic Variance-Reduced Policy Gradient

### 2018-02-09 svrpg.tex
stressed more the convergence rate

\begin{abstract}
        In this paper, we propose a novel reinforcement-learning algorithm consisting in a stochastic variance-reduced version of policy gradient for solving Markov Decision Processes (MDPs).
        Stochastic variance-reduced gradient (SVRG) methods have proven to be very successful in supervised learning.
        However, their adaptation to policy gradient is not straightforward and needs to account for I) a non-concave objective function; II) approximations in the full gradient computation; and III) a non-stationary sampling process.
        The result is SVRPG, a stochastic variance-reduced policy gradient algorithm that leverages on importance weight to preserve the unbiasedness of the gradient estimate.
        We further analyse its convergence guarantees under standard assumptions on the MDP.
        Finally, we suggest practical variants of SVRPG, and we empirically evaluate them on continuous MDPs.
\end{abstract}

@@

%Paper structure
After providing background on policy gradient and SVRG in Section \ref{sec:pre}, in Section \ref{sec:alg} propose SVRPG, a variant of SVRG for the policy gradient framework, addressing all the difficulties mentioned above. In Section \ref{sec:conv} we provide convergence guarantees for our algorithm which also offers insights on the challenges of variance reduction in RL. In Section \ref{sec:stopping} we suggest how to set the meta-parameters of SVRPG, while in Section \ref{sec:prac} we discuss some practical variants of the algorithm. Finally, in Section \ref{sec:exp} we empirically evaluate the performance of our method on popular continuous RL tasks.

@@

\begin{figure*}[t]
    \begin{minipage}[t]{0.32\textwidth}
	\includegraphics[width=.98\textwidth]{images/cart_pole_SVRPG_vs_GPOMDP_tex.pdf}
	\caption{On-line performance over sampled trajectories of SVRPG vs G(PO)MDP in the Cart-pole task, with 90\% t-student confidence intervals.}
	\label{fig:cartpole}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.32\textwidth}
	\includegraphics[width=0.98\textwidth]{swimmer_self_normalized_SVRPG_vs_SVRPG_tex.pdf}
	\caption{On-line performance over sampled trajectories of self-Normalized SVRPG vs unbiased SVRPG in the Swimmer task, with 90\% confidence intervals.}
	\label{fig:swimmertwo}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{.32\textwidth}
	\includegraphics[width=0.98\textwidth]{swimmer_self_normalized_SVRPG_vs_GPOMDP_tex.pdf}
	\caption{On-line performance over sampled trajectories of self-Normalized SVRPG vs G(PO)MDP in the Swimmer task, with 90\% confidence intervals}
	\label{fig:swimmerone}
    \end{minipage}
\end{figure*}

>>>>

\begin{abstract}
        In this paper, we propose a novel reinforcement-learning algorithm consisting in a stochastic variance-reduced version of policy gradient for solving Markov Decision Processes (MDPs).
        Stochastic variance-reduced gradient (SVRG) methods have proven to be very successful in supervised learning.
        However, their adaptation to policy gradient is not straightforward and needs to account for I) a non-concave objective function; II) approximations in the full gradient computation; and III) a non-stationary sampling process.
        The result is SVRPG, a stochastic variance-reduced policy gradient algorithm that leverages on importance weight to preserve the unbiasedness of the gradient estimate.
        {\color{blue}Under standard assumptions on the MDP, we provide convergence guarantees for SVRPG with a convergence rate that is linear under increasing batch sizes.}
        Finally, we suggest practical variants of SVRPG, and we empirically evaluate them on continuous MDPs.
\end{abstract}

@@

%Paper structure
After providing background on policy gradient and SVRG in Section \ref{sec:pre}, in Section \ref{sec:alg} propose SVRPG, a variant of SVRG for the policy gradient framework, addressing all the difficulties mentioned above. {\color{blue} In Section \ref{sec:conv} we provide convergence guarantees for our algorithm, and we show a convergence rate that has an $O(\nicefrac{1}{T})$ dependence on the number $T$ of iterations}. In Section \ref{sec:stopping} we suggest how to set the meta-parameters of SVRPG, while in Section \ref{sec:prac} we discuss some practical variants of the algorithm. Finally, in Section \ref{sec:exp} we empirically evaluate the performance of our method on popular continuous RL tasks.

@@

\begin{figure*}[t]
    \begin{minipage}[t]{0.32\textwidth}
	\includegraphics[width=.98\textwidth]{images/cart_pole_SVRPG_vs_GPOMDP_tex.pdf}
	\caption{On-line performance over sampled trajectories of SVRPG vs G(PO)MDP in the Cart-pole task, with 90\% confidence intervals.}
	\label{fig:cartpole}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.32\textwidth}
	\includegraphics[width=0.98\textwidth]{swimmer_self_normalized_SVRPG_vs_SVRPG_tex.pdf}
	\caption{On-line performance over sampled trajectories of self-Normalized SVRPG vs unbiased SVRPG in the Swimmer task, with 90\% confidence intervals.}
	\label{fig:swimmertwo}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{.32\textwidth}
	\includegraphics[width=0.98\textwidth]{swimmer_self_normalized_SVRPG_vs_GPOMDP_tex.pdf}
	\caption{On-line performance over sampled trajectories of self-Normalized SVRPG vs G(PO)MDP in the Swimmer task, with 90\% confidence intervals}
	\label{fig:swimmerone}
    \end{minipage}
\end{figure*}
